

\documentclass["../Applied_probabillity _and_statistics_lab_KTU.tex"]{subfiles}
 
\begin{document}
      I was a member of syllabus revision committee for Master of Computer Applications(MCA) Course  offered by  Kerala Technological university during 2016. During the committee meeting Prof Jyothi John ( Principal College of Engineering  Chengannur) suggested the inclusion of applied statistics and probability theory as a core paper. It was also proposed  that a supporting lab course  also be  offered. I was entrusted with formulating the syllabus for both. 
       
       For  theory classes there are several excellent text books available.  For laboratory classes there was a little bit of confusion in the committee . There are several options avoidable for experimenting with statistics.   However, most of the commercial statistics packages  are proprietary and costly.  I suggested the use of R for the class, as R is being extensively used as a prferred tool by data sciences community.  However  several members felt that there was no good laboratory manuals for  teaching the basics. It  was also pointed out that students pursuing   MCA come from a variety of backgrounds such as science and commerce. 
       
       I promised to write some introductory material so that students  and  faculty can use it for their lab practice. The material presented is  an early draft and should be used with caution. It needs lot of editing and  correction. This manual uses ideas and code taken from many sources. I will try to attribute credits as far as possible in the final version. Since the course has started in several affiliated colleges, there was some urgenty in releasing the material. Hence, several fine points may be missing.   Any errors found in the draft may be  sent to me via email at vu2swx  at gmail dot com
       It is suggested that students use the R studio environment rather than vanilla R console. The R studio is user friendly and intuitive.
       
 
\end{document}


